### 2021-10-08 paper/pldi22/abstract.tex
Abstract

\begin{abstract}\label{sec:abstract}
  \todo
\end{abstract}

>>>>

\begin{abstract}\label{sec:abstract}
  JavaScript is a widely-used programming language in various fields.  Recently,
  it rapidly evolves with a yearly release cadence and open development process
  to quickly adapt users' demands to the language.  In this fast-evolving nature
  of JavaScript, the need of \textit{language design assistants} has grown to
  correctly understand original or revised semantics in the revision process.
  While several tools have been proposed as language design assistants for
  JavaScript in academia and industry, they should be manually updated to
  represent revised semantics and lack the information for better comprehension
  of language semantics.  To alleviate this problem, we present $\tool$, the
  first language design assistant for JavaScript that directly synchronizes with
  language specification and even conformance tests. Moreover, our tool provides
  a way to focus on specific semantics by automatically reducing semantics and
  filtering out conformance tests with \textit{syntactic views}. In this paper,
  we conduct several case studies for the JavaScript language design with
  $\tool$. Moreover, we evaluate how effectively do syntactic views reduce the
  semantics and filtering out conformance tests.
\end{abstract}
